%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rishi Shah 
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style
\usepackage{hyperref}

\usepackage[left=0.61in,top=0.3in,right=0.61in,bottom=0.4in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Iago Calvo Lista} % Your name
\address{Horsham RH12 2PD, United Kingdom} % Your address
\address{\href{mailto:iagocltrabajo@gmail.com}{iagocltrabajo@gmail.com} - \url{https://github.com/iagoCL}} % Your phone number and email
%\address{Minimum salary 60.000 \pounds} % Your phone number and email

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------
\begin{mainSection}{Work Experience}
\begin{multiWorkExperience}
{Gameplay Programmer}{Creative Assembly (SEGA)}{Horsham, UK}{Sep 2020}{Present}
\item Worked in \textbf{Total War: Warhammer 3} a popular RTS with over 150.000 concurrent users.

\item Promoted from Trainee and Associate Gameplay Programmer to responsible for battle gameplay in DLCs.

\item Increased stability by fixing 400+ bugs, debugging with \textbf{Visual Studio} and writing maintainable \textbf{C++}.

\item Improved performance by detecting and \textbf{optimizing} critical areas, with custom and standard \textbf{profilers}

\item Reduced time to fix bugs by replacing old code with \textbf{modern C++}, which improved code readability.

\item Removed recurrent bugs by adding \textbf{automatic testing} which successfully detected 500 data problems.

\item Increased QA efficiency by adding custom debug functionality and improving internal logging.

\item Responsible for communication across multiple departments, to coordinate new features and bug-fixing.

\item Followed \textbf{Agile}(\textbf{Scrum}) using \textbf{Jira}, perforce (\textbf{version control}) and \textbf{continuous integration}.
\end{multiWorkExperience}
\begin{multiWorkExperience}
{Research Support Staff/C++ Programmer}{GMRV}{Madrid, Spain}{Nov 2017}{Jul 2019}

\item Group of Modeling and Virtual Reality (GMRV) in King Juan Carlos University.

\item European project funded by the \textit{Human Brain Project (HBP)} and \textit{Cajal Blue Brain}.

\item Secondary author of the research article \url{https://doi.org/10.3389/fninf.2021.766697}.

\item Development and \textbf{optimization} of \textit{NeuroScheme}, an \textbf{open-source} data-science visualization application.

\item Increased performance by using \textbf{C++} and \textbf{Qt} to \textbf{parallelise} the application.

\item Improved the user experience by improving the UI and supporting new file formats.

\item Followed \textbf{Agile} methodology with \textbf{git}(version control) developing a \textbf{Windows}/\textbf{Linux} application.
\end{multiWorkExperience}
\end{mainSection}
\begin{mainSection}{Education}
\begin{educationItem}
{MSc in High-Performance Computing with Data Science}{Sep 2019}{Aug 2020}{University of Edinburgh}{Scotland, United Kingdom}

\item GPA: 68/100 2:1 Honours.

\item Selected as one of 5 members of TeamEPCC, reaching 5\textsuperscript{th} position at the international \textbf{ISC - SCC (2020)}.% and 3\textsuperscript{rd} popular vote

\item Emphasis on \textbf{parallelism}, including \textbf{multithreading}, concurrency, multiprocessor, message passing (MPI).

\item Extensive use of \textbf{C} to design \textbf{HPC} systems including \textbf{IO}, memory optimisations and profiling.
\end{educationItem}
\begin{educationItem}
{Dual degree in Game Design and Development and Computer Engineering}{Sep 2015}{Aug 2019}{Universidad Rey Juan Carlos (King Juan Carlos University)}{Madrid, Spain}

\item GPA: 8.02 / 10.00 (B+). Equivalent to two 2:1 UK BSc honours degrees.

\item \textbf{Computer networks} including \textbf{sockets}, distributed systems (\textbf{AWS}, \textbf{Docker}) and routing optimisation.

\item Emphasis on \textbf{computer hardware} architecture (\textbf{assembly}, embedded systems and hardware design).

\item Advanced courses in \textbf{OOP}, \textbf{algorithms design}, \textbf{data structures} and \textbf{design patterns}

\item Graphics (\textbf{OpenGL}, \textbf{Vulcan}, GPGPU (\textbf{cuda})) and operating systems (\textbf{Linux}, \textbf{Android}, virtualisation)

\item Experience in databases, \textbf{SQL} and \textbf{NoSQL} (\textbf{MongoDB}, Cassandra)

\item Multiple individuals and group projects in \textbf{C}, \textbf{C++} \textbf{Java}, \textbf{Javascript}, \textbf{C\#} and \textbf{python}, see link below.
\end{educationItem}
\end{mainSection}
\begin{mainSection}{Technical skills}
\begin{tabular}{ @{} >{\bfseries}l @{\hspace{4ex}} l }
Programming\ & \textbf{C}, \textbf{C++}, JavaScript, Python, Java, C\# \\
Web \ &  HTML5, CSS, Spring, PHP \\
Abilities\ & \textbf{Linux}, \textbf{Parallelism}, Multithreading, Concurrency, IO, Databases, Graphics \\
Other \ &   \textbf{Cmake}, \textbf{make}, \textbf{Git}, \textbf{CI}, \textbf{Visual Studio}, Agile, JIRA
\end{tabular}

Please visit: \url{https://iagocl.github.io/portfolio} for more information and see my personal projects.
\end{mainSection}

\begin{mainSection}{Languages}

\begin{languageItem}{Spanish}{Native speaker.}
\end{languageItem}
\begin{languageItem}{English}{Fluent speaker.}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{16ex}} l @{\hspace{22ex}} >{\it}l}
IELTS Academic \ & C1 \ & May 2019 \\
Cambridge Proficiency exam (CPE) \ & C1 \ & June 2017
\end{tabular}
\end{languageItem}
\end{mainSection}
%\begin{mainSection}{Extra-Curricular} \itemsep -14pt
%\item\textbf{ Music Elementary Degree} (\textbf{Piano}): Center of Musical Studies M Peleteiro, Santiago Compostela, Spain.
%\end{mainSection}
\end{document}